Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-07-08 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
revised paper and letter
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\textcolor{blue}{On the left side of Fig.~\ref{fig:flow}, we describe the needed \textbf{inputs} to size a PV system. There exist requirements from the house to be electrified; in particular, we have the design assumptions, weather information from the targeted local of the PV system deployment, and a possible initial list of equipment to be used, covering all the items listed in Fig.\ref{fig:blockdiagram}. Concerning the equipment list, the designer can use a few equipments or a vast one. We can also decide not to adopt the commercial equipment list. However, the result is a PV sizing of specific power, current, or voltage values, and usually just close to original equipment, which can be found in the market. This possibility has the drawback of possible incompatibility among equipment when the real one is bought and deployed.}

@@

\noindent where $C_{PV}$ is the PV array cost, $C_{bat}$ is the initial cost of batteries, $C_{charger}$ is the cost of the charger, $C_{inv}$ is the inverter cost, $C_{installation}$ is the installation cost, $C_{batrep}$ is battery replacement cost at current prices, and $C_{PWO\&M}$ is operation and maintenance costs at current rates. \textcolor{blue}{In this study, we will use a $C_{installation}$ equivalent to 5\% of total equipment cost and a $C_{PWO\&M}$ equal to U\$ 289.64/year according to Amazon State literature data~\cite{Agrener2013}; and a LCC lifetime analysis of 20 years.}

@@

Each simulation with PVsyst took $4$ seconds. We were unable to validate case study $3$ using PVsyst since the battery autonomy is less than 24 hours, and only the proposed synthesis technique can perform the optimal sizing (PVsyst and HOMER Pro are limited for a $24$ h minimum). Case studies $2$ and $7$ had only HOMER Pro sizing validation. There is no deployed equivalent system in the field, and the synthesis technique did not present a solution due to \textit{time out} and internal failures in the underlying verification engine. %(our technique presented a \textit{time out} in case study $2$ and an \textit{UNSAT} in the case study $7$).

@@

\textcolor{blue}{Note that an optimal solution from a tool is not necessarily the same optimal from other tools, mainly when the database of equipment items (with different costs) are not the same \cite{Alsadi2018}. Therefore, the comparison must take this issue into account.}

@@

We have reported a favorable assessment of the proposed method. Nevertheless, we have also identified four threats to the validity of our results that constitute future work. First, improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the study more accurate. Second, improvement of the system cost analysis by adding operational and maintenance costs to the adopted LCC analysis. Third, increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing. Lastly, the underlying software verifiers employed here perform bit-precise verification based on the Floating-Point (FP) theory. We could use a real arithmetic strategy to tackle these equations; however, in this study, we have exploited the FP arithmetic, which approximates the real one.

@@

%
% ---- Bibliography ----
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{trindadeThesis}
%
\end{document}
%\subsection{Design and Simulation of Solar PV systems}
%The design and validation of a PV system can be done by hand or with the aid of a software tool. In order to address different aspects of the PV system design, there are various software tools available in the literature~\cite{Rajanna,Rawat}.
%public domain and commercial software available for the PV market. 
%According to \cite{Brooks}, t
%%%%%%%%%%
%
%The capabilities of tools available in the literature range from simple solar resource and %energy production estimation, %to site survey and system design tools,
%to complex financial analysis and project optimization. At this study, the commercial simulation tool HOMER PRO was selected to be used at the case studies in order to be compared with the automated verification tools.

>>>>

\textcolor{blue}{On the left side of Fig.~\ref{fig:flow}, we describe the needed \textbf{inputs} to size a PV system. There exist requirements from the house to be electrified; in particular, we have the design assumptions, weather information from the targeted local of the PV system deployment, and a possible initial list of equipment to be used, covering all the items listed in Fig.\ref{fig:blockdiagram}. Concerning the equipment list, the designer can use a few pieces of equipment or a vast one. We can also decide not to adopt the commercial equipment list. However, the result is a PV sizing of specific power, current, or voltage values, and usually just close to original equipment, which can be found in the market. This possibility has the drawback of possible incompatibility among equipment when the real one is bought and deployed.}

@@

\noindent where $C_{PV}$ is the PV array cost, $C_{bat}$ is the initial cost of batteries, $C_{charger}$ is the cost of the charger, $C_{inv}$ is the inverter cost, $C_{installation}$ is the installation cost, $C_{batrep}$ is battery replacement cost at current prices, and $C_{PWO\&M}$ is operation and maintenance costs at current rates. \textcolor{blue}{In this study, we will use a $C_{installation}$ equivalent to 5\% of total equipment cost and a $C_{PWO\&M}$ equal to U\$ 289.64/year according to Amazon State literature data~\cite{Agrener2013}; and an LCC lifetime analysis of 20 years.}

@@

Each simulation with PVsyst took $4$ seconds. We were unable to validate the case study $3$ using PVsyst. The battery autonomy is less than 24 hours, and only the proposed synthesis technique can perform the optimal sizing (PVsyst and HOMER Pro are limited for a $24$ h minimum). Case studies $2$ and $7$ had only HOMER Pro sizing validation. There is no deployed equivalent system in the field, and the synthesis technique did not present a solution due to \textit{time out} and internal failures in the underlying verification engine. %(our technique presented a \textit{time out} in case study $2$ and an \textit{UNSAT} in the case study $7$).

@@

\textcolor{blue}{Note that an optimal solution from a tool is not necessarily the same optimal from other tools, mainly when the database of equipment items (with different costs) is not the same \cite{Alsadi2018}. Therefore, the comparison must take this issue into account.}

@@

We have reported a favorable assessment of the proposed method. Nevertheless, we have also identified four threats to the validity of our results that constitute future work. First, improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the study more accurate. Second, improvement of the system cost analysis by adding operational and maintenance costs to the adopted LCC analysis. Third, increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing. Lastly, the underlying software verifiers employed here perform bit-precise verification based on the Floating-Point (FP) theory. We could use a real arithmetic strategy to tackle these equations; however, in this study, we have exploited the FP arithmetic, approximating the real one.

@@

%
% ---- Bibliography ----
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{trindadeThesis}

%
\end{document}
%\subsection{Design and Simulation of Solar PV systems}
%The design and validation of a PV system can be done by hand or with the aid of a software tool. In order to address different aspects of the PV system design, there are various software tools available in the literature~\cite{Rajanna,Rawat}.
%public domain and commercial software available for the PV market. 
%According to \cite{Brooks}, t
%%%%%%%%%%
%
%The capabilities of tools available in the literature range from simple solar resource and %energy production estimation, %to site survey and system design tools,
%to complex financial analysis and project optimization. At this study, the commercial simulation tool HOMER PRO was selected to be used at the case studies in order to be compared with the automated verification tools.

### 2020-07-08 Tex/CAV2019/replyVSTTEJUNE2020.tex
revised paper and letter
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

%\vi

%Thank you very much in advance.

@@

Algorithm 1 to me seems to construct a constraint and then tries to solve it for the nondeterministic variables to obtain a solution, and to use essentially a linear search to find the minimum cost. Is this correct? If so, it is unclear to me how this fits with the CEGIS algorithm in Fig. 2, and where model checking is used.

\begin{resposta} 
We use four non-deterministic variables to index four matrices with complete datasheet information from an equipment item. We have four variables and four matrices: one to PV panels, one to batteries, one to the inverter, and one to the charge controller. Those non-deterministic variables are used during the search for the feasible solution and controlled by the statements \textbf{assume}. The candidate solution is proposed in the phase {\sc Synthesize} of the technique. For the {\sc Verify} phase, we performed a linear search for the lowest cost, and the result is based on FAIL or SUCCESS check from a cost that is linearly incremented in this model. The model checking is used during this {\sc Verify} phase. If the process produces FAIL, then an optimal solution is found. If SUCCESS is presented, i.e. the property holds, there is no feasible solution from the equipment list provided by the technique. \textcolor{red}{This explanation was included at page 9, in the end of section "Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems".}
We added a future work at the end of the CONCLUSIONS section as well, related to the possibility of speeding up the {\sc Verify} phase through binary search or even using specific optimization targeted solvers (as $\nu Z$).
\end{resposta}

@@

\begin{resposta} 
We thank the reviewer for this insightful comment and suggestion. You are correct; Reviewer \#1 also provided the same observation. We had to revise the Background, and the Synthesizing Optimal Sizing sections in order to address the right conference attendants profile. Our manuscript was revised, and the PV sizing modeling was changed to a higher level of explanation, including a flowchart in Section 2 (cf. Figure 4). In Section 3, the synthesis algorithm followed the same idea. Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF complementary file that can be accessed as well.
\end{resposta}

@@

\begin{resposta}
We have updated the entire paragraph in the complementary online file to explain the meaning of these variables. ``The short circuit reference information ($I_{sc,ref}$) from the manufacturer's solar panel must be corrected because field temperature ($T$) is higher than nominal or laboratory temperature ($25^{\circ}C$), and the PV system is temperature dependent, as described by Eq. (9) for the ambient short-circuit current from the PV panel. $G$ is the solar irradiance from the deployment site, and $G_{ref}$ is defined as $1000$ $W/m^{2}$ by the manufacturers.''
\end{resposta}

@@

\begin{resposta} 
We thank the reviewer for these insightful comments and suggestions. Those are the same observations did by Reviewer \#1 and \#2. We had to revise the Background, and the Synthesizing Optimal Sizing sections in order to address the right conference attendants profile. Our manuscript was revised, and the PV sizing modeling was changed to a higher level of explanation, including a flowchart in Section 2 (cf. Figure 4). In Section 3, the synthesis algorithm followed the same idea. Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF complementary file that can be accessed as well.
\end{resposta}

@@

% \printbibliography
\end{document}

>>>>

@@

Algorithm 1 to me seems to construct a constraint and then tries to solve it for the non-deterministic variables to obtain a solution, and to use essentially a linear search to find the minimum cost. Is this correct? If so, it is unclear to me how this fits with the CEGIS algorithm in Fig. 2, and where model checking is used.

\begin{resposta} 
We use four non-deterministic variables to index four matrices with complete datasheet information from an equipment item. We have four variables and four matrices: one to PV panels, one to batteries, one to the inverter, and one to the charge controller. Those non-deterministic variables are used during the search for the feasible solution and controlled by the statements \textbf{assume}. The candidate solution is proposed in the phase {\sc Synthesize} of the technique. For the {\sc Verify} phase, we performed a linear search for the lowest cost, and the result is based on FAIL or SUCCESS check from a cost that is linearly incremented in this model. The model checking is used during this {\sc Verify} phase. If the process produces FAIL, then an optimal solution is found. If SUCCESS is presented, i.e., the property holds, there is no feasible solution from the equipment list provided by the technique. This explanation was included at the end of the section ``Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems". We added a future work at the end of the Conclusions section concerning the possibility of speeding up the {\sc Verify} phase through binary search or even using specific optimization targeted solvers (as $\nu Z$).
\end{resposta}

@@

\begin{resposta} 
We thank the reviewer for this insightful comment and suggestion. You are correct; Reviewer \#1 also provided the same observation. We had to revise the Background, and the Synthesizing Optimal Sizing sections to address the right conference attendants profile. Our manuscript was revised, and the PV sizing modeling was changed to a higher level of explanation, including a flowchart in Section 2 (cf. Figure 4). In Section 3, the synthesis algorithm followed the same idea. Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF complementary file that can be accessed.
\end{resposta}

@@

\begin{resposta}
We have updated the entire paragraph in the complimentary online file to explain the meaning of these variables. ``The short circuit reference information ($I_{sc,ref}$) from the manufacturer's solar panel must be corrected because field temperature ($T$) is higher than nominal or laboratory temperature ($25^{\circ}C$), and the PV system is temperature dependent, as described by Eq. (9) for the ambient short-circuit current from the PV panel. $G$ is the solar irradiance from the deployment site, and $G_{ref}$ is defined as $1000$ $W/m^{2}$ by the manufacturers.''
\end{resposta}

@@

\begin{resposta} 
We thank the reviewer for these insightful comments and suggestions. Those are the same observations did by Reviewer \#1 and \#2. We had to revise the Background, and the Synthesizing Optimal Sizing sections to address the right conference attendants profile. Our manuscript was revised, and the PV sizing modeling was changed to a higher level of explanation, including a flowchart in Section 2 (cf. Figure 4). In Section 3, the synthesis algorithm followed the same idea. Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF complementary file that can be accessed as well.
\end{resposta}

@@

\end{document}
